\section*{Journal Publications}
\begin{enumerate}
	\item Jingwei Zhang*, {\bf Lei Tai}*, Peng Yun, Yufeng Xiong, Ming Liu, Joschka Boedecker, Wolfram Burgard, ``VR-Goggles for Robots: Real-to-sim Domain Adaptation for Visual Control", (* indicates equal contribution), \emph{IEEE Robotics and Automation Letters (RA-L)}, 2019.
  \item Peng Yun, {\bf Lei Tai}, Yuan Wang, Ming Liu, ``Focal Loss in 3D Object Detection", \emph{IEEE Robotics and Automation Letters (RA-L)}, 2019.
  \item {\bf Lei Tai}, Shaohua Li, Ming Liu, ``Autonomous Exploration of Mobile Robots through Deep Neural Networks", \emph{International Journal of Advanced Robotic Systems (IJARS)}, 2017.
  \item {\bf Lei Tai}, Ming Liu, ``Mobile Robots Exploration through CNN-based Reinforcement Learning", \emph{Robotics and Biomimetics}, 2016.
\end{enumerate}
\section*{Conference Publications}
\begin{enumerate}
	\item {\bf Lei Tai}, Peng Yun, Yuying Chen, Congcong Liu, Haoyang Ye, Ming Liu ``Visual-Based Autonomous Driving Deployment from a Stochastic and Uncertainty-Aware Perspective", \emph{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, Macau, China, November 4-8, 2019.
	\item Yuying Chen*, Congcong Liu*, {\bf Lei Tai}, Ming Liu, Bertram Shi ``Gaze Training by Modulated Dropout Improves Imitation Learning", \emph{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, Macau, China, November 4-8, 2019.
	\item Congcong Liu*, Yuying Chen*, {\bf Lei Tai}, Haoyang Ye, Ming Liu, Bertram Shi, ``A Gaze Model Improves Autonomous Driving", \emph{ACM Symposium on Eye Tracking Research \& Applications (ETRA)}, Denver, USA, June 25-28, 2019.
	\item {\bf Lei Tai}, Jingwei Zhang, Ming Liu, Wolfram Burgard, ``Socially-compliant Navigation through Raw Depth Inputs with Generative Adversarial Imitation Learning", \emph{International Conference on Robotics and Automation (ICRA)}, Brisbane, Australia, May 21-25, 2018.
	\item {\bf Lei Tai}, Giuseppe Paolo, and Ming Liu, ``Virtual-to-real Deep Reinforcement Learning: Continuous Control of Mobile Robots for Mapless Navigation, \emph{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, Vancuver, Canada, September 24-28, 2017.
	\item {\bf Lei Tai}, Haoyang Ye, Qiong Ye, Ming Liu, ``PCA-aided Fully Convolutional Networks for Semantic Segmentation of Multi-channel fMRI", \emph{International Conference on Advanced Robotics (ICAR)}, Hong Kong, China, July 10-12, 2017.
  \item {\bf Lei Tai}, Shaohua Li, and Ming Liu, ``A Deep-Network Solution Towards Model-less Obstacle Avoidence", \emph{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, Daejeon, Korea, October 9-14, 2016.
  \item {\bf Lei Tai}, Ming Liu, ``A Robot Exploration Strategy Based on Q-learning Network", \emph{IEEE International Conference on Real-time Computing and Robotics (RCAR)}, Angkor Wat, Cambodia, June 6-10, 2016.
\end{enumerate}
\section*{Workshop Publications}
\begin{enumerate}
	\item Congcong Liu*, Yuying Chen*, {\bf Lei Tai}, Ming Liu, Bertram Shi, ``Utilizing Eye Gaze to Enhance the Generalization of Imitation Network to Unseen Environments", \emph{International Conference on Machine Learning (ICML) Workshop}, June 14, Long Beach, USA, 2019.
	\item Oleksii Zhelo, Jingwei Zhang, {\bf Lei Tai}, Ming Liu, Wolfram Burgard, ``Curiosity-driven Exploration for Mapless Navigation with Deep Reinforcement Learning", \emph{International Conference on Robotics and Automation (ICRA) Workshop}, May 21, Brisbane, Australia, 2018.
\end{enumerate}
\section*{Technical Reports}
\begin{enumerate}
	\item {\bf Lei Tai}*, Jingwei Zhang*, Ming Liu, Joschka Boedecker, Wolfram Burgard, ``A Survey of Deep Network Solutions for Learning Control in Robotics: From Reinforcement to Imitation", (* indicates equal contribution).
	\item Jingwei Zhang, {\bf Lei Tai}, Joschka Boedecker, Wolfram Burgard, Ming Liu, ``Neural SLAM: Learning to Explore with External Memory".
	\item {\bf Lei Tai}, Ming Liu, ``Towards cognitive exploration through deep reinforcement learning for mobile robots".
\end{enumerate}
